Blocking-resistant communication through high-value web services

### 2014-07-08 docs/meek.tex
Remember Psiphon.
Entry+exit observation.

@@

@@

The deployment we envision and have started to implement
uses a single paid App Engine instance, which is publicly known and usable by anyone.
Client software is configured to use this public instance by default.
A preconfigured public instance has great usability advantages
because there is nothing for the user to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to Tor bridge now includes App Engine and the web app operators,
in addition to the ISP and intermediate routers that were there before.
On the other hand, the Tor bridge no longer gets to see users' IP addresses:
all it sees are many connections from App Engine.
In effect, App Engine and the web app become what Tor calls a ``guard node,''
a privileged relay that takes the first hop in the chain of relays.
Because Tor is encrypted and integrity-protected, neither App Engine nor the app operators
are able to read or alter users' communications, but being on path enables them
to do things like measure packet timing patterns.

>>>>

When domain fronting is combined with Tor,
the CDN or web service effectively becomes
what Tor calls a ``guard node,''
a host with a privileged network position that can observe
the ciphertext entering the network.
One consequence of this fact is that Google (for example)
knows the IP addresses of everyone using the circumvention system,
just as if it were those users' ISP.
Another consequence is that the CDN or web service gets
to observe and correlate both entry and exit traffic,
in the special case where the target of the communication
also lies on the same CDN or web service.
For example, a user fronting through App Engine and
browsing YouTube reveals both their entry and exit traffic to Google,
which may attempt through traffic analysis to determine
which entry packets correspond to which exit packets.
The problem is hard to counter, because the front domain needs
to be a popular destination in order to have high collateral damage,
but popular destinations by definition tend to be visited a lot.
% Possible countermeasure is traffic fingerprinting resistance
% like what mjuarez is working on, mostly orthogonal to circumvention.

@@

% Psiphon

@@

The deployment we envision and have started to implement
uses a single paid App Engine instance, which is publicly known and usable by anyone.
Client software is configured to use this public instance by default.
A preconfigured public instance has great usability advantages
because there is nothing for the user to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to Tor bridge now includes App Engine and the web app operators,
in addition to the ISP and intermediate routers that were there before.
On the other hand, the Tor bridge no longer gets to see users' IP addresses:
all it sees are many connections from App Engine.
